\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{glossaries}

\geometry{ margin=1in }

\makeglossaries

\newglossaryentry{ASIC}
{
    name=ASIC,
    description={Application Specific Integrated Circuit. Often used to mine
    cryptocurrencies, the most prominent being bitcoin}
}

\newglossaryentry{segwit}
{
    name=Segwit,
    description={Freeing block size limit by segragating signature (witness)
    data}
}

\newglossaryentry{mempool}
{
    name=Mempool,
    description={Pool of all entries that want to be included in a block}
}

\title{
    PADLOCK \\
    \large Protocol Allowing for Decentralized Locking/Ownership of C-hashes to
    K-public keys
}
\author{Ellis Frank}

\begin{document}

\maketitle

\begin{abstract}
    PADLOCK is a blockchain based protocol that allows for the
    creation of a scalable and private cryptocurrency. It achieves this by only
    storing a hash of the input and the output, a hash of the signature, and
    then an 8 byte anti-spam proof of work. This process is than publicly disclosed on the blockchain in order to verify that the coin is not being double-spent. 
    This results in a minimal transaction size of only 56 bytes, allowing for
    roughly 4x more throughput than bitcoin.
\end{abstract}

\section{Introduction}
PADLOCK is a blockchain based system that allows the
ownership and transfer of hashes by key pairs. The purpose of this hash
ownership is to provide the base for creating a scalable and private currency
that runs on top of the PADLOCK blockchain. This paper assumes a general
understanding of how traditional cryptocurrencies work.

\section{How Does PADLOCK Work?}
PADLOCK uses digital signatures to facilitate the ownership of hashes. However,
it does so differently than contemporary cryptocurrencies. Only a hash of the signature is
stored on-chain, and the public key is left off-chain. Alongside the signature
hash, is an input hash, an output hash, and a proof of work. These four aspects together,
make up an \textit{entry}.

\begin{verbatim}

\\ Example written in Rust

type Hash = [u8; 16];

struct Entry {
    input: Hash,
    output: Hash,
    signature_hash: Hash,
}

\end{verbatim}

Anyone can submit an entry to the blockchain. They do not have to provide any
sort of signature, just an object of three 16 byte arrays. This provides a base
for creating a scalable, private, and consistent (meaning no double-spending) cryptocurrency.

\section{Creating Coins on PADLOCK}

\subsection{What is a Coin}
It's important to make a distinction between crypto and non-crypto currencies when talking about currencies in this context.
Coins, in this context, do not refer to a unit of currency, but rather a chain
of digital signatures. When you transfer a coin, you are appending a signature
to this history. Each transaction has an \textit{input} and an \textit{output}. The
input is the hash of the transaction's sender, and the output of the
recipient(s) of the coin. The input is represented as the hash of the previous
transaction.

\begin{verbatim}

\\ Example written in Rust
struct Coin {
    transactions: Vec<Transaction>,
}

struct Transaction {
    input_hash: Hash,
    output: Vec<PublicKey>,
    hash: Hash,
    signature: [u8; 64],
}

\end{verbatim}

This coin can be divided into multiple fractions of a coin, specifying more than one
public key as the owner. Each coin is then representing a fraction of the value of the
original coin. When a transaction occurs, the sender can send a
fraction of the coin to the receiver, and the rest back to themselves, much like change in the real world.

The \textit{coinfile} is a file that contains the history of a coin, back to
it's minting.

\subsection{The Double Spend Problem}
These coins, on their own, do not work as a currency. The receiver of a coin
does not know whether the sender has already spent that coin. If Alice has a
coin, she can create a transaction giving ownership to Bob on her coinfile, and
send that to Bob, then use the same coin to send one to Tom, and unless Tom and
Bob know each other, there is no way for either of them to know Alice has spent
the coin twice.

\subsubsection{How it has been traditionally solved}
Traditional cryptocurrencies solve this problem by having every coins history be
disclosed publicly on a blockchain. Transactions are only allowed on the
blockchain if the sender has not already spent the output that is being used as
the input.

\subsubsection{The Issue With This Solution}
The issue, is that hosting a full node can take a lot of disk space
and bandwidth. At the time of writing this, the bitcoin blockchain is 310
gigabytes. It grows at approximately 200 megabytes per day when at max
capacity. The block size is capped out at around 1.3-1.6 megabytes (although
it's variable due to \gls{segwit}) in order to prevent the blockchain from getting too
big, too quick.  This causes for a bottleneck to occur, where there are more
transactions wanting to confirm, than can fit in too the next block, or even the
next 5, 10, or at the time of writing this, 40 blocks. Because transaction fees
are privy to supply and demand trends, the fees spike. At the time
of writing this, a low priority transaction takes approximately \$4.5 USD, and in
order to be included in the next block, you must pay around \$7.5 USD in fees.

One solution that has been tried is merely increasing the block size limit.
This means more transaction can be included in the next block, getting rid of
the bottleneck that is encountered in traditional cryptocurrencies. This however, leads to centralization issues. Due to the
increasing storage and bandwidth requirements, hosting a full node will become
infeasible for the vast majority of people, and will only be aquired by a select few.

A better solution is to include as many transactions as possible in the limited
amount of space each block has. In order to do that, you have to decrease the
amount of storage each transaction takes up. Under PADLOCK, each transaction
takes only 48 bytes minimum, compared to the ~190 byte minimum on bitcoin
(including witness data). This results in nearly 4x more throughput when using
the PADLOCK system.

\subsection{How PADLOCK Solves the Double Spend Problem}
PADLOCK solves it by having each transaction of a coin have it's input, output,
and signature hashed, and then used as an entry on the PADLOCK blockchain.
At a basic level, one can verify whether a coin has already been spent by
hashing the input of the transaction sent to them, and then verifying wether or not the input
has been used on any entries in the blockchain. If it has, it would be known that
the coin had already been spent, and the transaction would terminate.

This still doesn't work. Because anyone can make an entry, a fraudelent body could make an entry that uses an unspent output that doesn't belong to
them. A solution to this, however, would be to have the full signature and public key be
apart of each entry. This would result in transactions taking up significantly
more space (128 bytes if using ed25519).

One optimization would be to remove the public key from the entries, resulting
in a 96 byte single-input, single-output transaction. One could make a fake
entry spending an output that doesn't belong to them, however, a receiver of a
transaction could easily verify whether the fake transaction was real, by
checking the signature against the public key of the sender.

To even further the optimization, you can replace the signature with a 16 byte
hash of the signature. Before sending the coinfile with the appended
transaction to the receiver, the sender would first have to scan the blockchain
to see if there are any fake transactions spending their output(s). If there
are, the sender would have to make a signature of each of these, and list them
in the new transaction. The receiver would then be able to hash each of these,
and verify that these hashes don't match the ones on chain. They would then know
that the coin(s) being sent to them have not already been spent.

\subsubsection{A Potential Attack to This System, And A Solution to the Attack}
One way to attack this problem would go as follows:

\begin{enumerate}
    \item Make a transaction that would all of public key A's coins to you. Do
        not worry about the signature for now.
    \item Put an entry on the blockchain for this transaction.
    \item Get A to make a transaction sending you coins.
    \item In the transaction they send you, they would have to include a
        signature of the fake transaction you made.
    \item You can now broadcast the fake transaction with the signature, and
        steal A's coins.
\end{enumerate}

In order to provide a feasible solution, to make a transaction, you would have to make
two signatures. One of the transaction itself, and then one of the entry on the
blockchain (not including the signature hash of course). This means that
despite having a signature for the transaction, the bad actor shown before
would not have a valid signature for the on-chain entry, meaning that if they
go to send their newly acquired coins to someone, the receiver could tell that
the sender made a fake transaction to acquire those coins.

\subsection{Issuance}
Issuance can be done via the 256 byte miner address field in the block header.
Miners can feel free to include whatever they please in this field. Generally,
though they'd want to include some sort of address. A coin could then allow
using the miner address as an input to a transaction.

\section{ASIC Resistance}
The proof of work algorithm used by PADLOCK should be \Gls{ASIC} resistant.
\Gls{ASIC} resistance is desirable because \Gls{ASIC} mining greatly increases
the barrier to entry for mining, making it inaccessible for a broader background of people, and
centralizing mining.

In order to achieve \Gls{ASIC} resistance, PADLOCK will cycle through different
mining algorithms. This makes it uneconomical for miners to invest in
\Gls{ASIC}, as those \Gls{ASIC} will become useless after PADLOCK switches
algorithms.  However, those algorithms could be utilized by other
cryptocurrencies, so an\Gls{ASIC}  miner could simply switch to a different
cryptocurrency to mine.  This makes it important to use mining algorithms that
are entirely new, or use old ones that are tweaked, to make them incompatible
with \Gls{ASIC} specifically designed for those algorithms.

\section{Privacy}
Privacy is achieved first by pseudonymity. Transactions are associated with
a public key, rather than their true identity. Of course, the issue there is
that if someone managed to trace a public key back to a real person, that
persons transactions would be publicly known, making central aspects of cryptocurrencies obsolete.

A common way to combat that is by sending the change of each transaction to a
new public key. For example, say Alice sends 20 coins to Bob, from her public
key, A. A has 30 coins belonging to it. When she sends the transaction to Bob,
instead of sending the remaining 10 coins back to public key A, she makes a new
public key, B, and sends the 10 coins to that. To an outsider, they are unable
to tell which public key was Alice's, and which was Bob's.

PADLOCK further combats this by not having every transaction publicly
available. Instead, they are all in each coinfile. Someone who possess a
coinfile would be able to see many transactions, but it would be made incredibly
hard to piece together the entire history of all the transactions, and then link that sequence back to a public key. This
drastically increases the extent of PADLOCK's privacy.

\section{Anti-Spam Measures}
It would be possible to execute a denial of service attack on PADLOCK by simply
filling the \gls{mempool} with meaningless entries. It would then make it
increasingly unlikely that the legitimate entries would be added to a block.
Most cryptocurrencies use a transaction fee, which makes it very uneconomical
for an attacker to create enough transactions to fill the \gls{mempool}.
Transaction fees are infeasible to implement under PADLOCK, however. It would
involve sending many gigabytes worth of coinfiles to
the miner, which would take up immense bandwidth and storage.

Instead, on PADLOCK, each transaction must submit a proof of work. The proof of
work algorithm for this will be very similar to hashcash. You must make an md5
hash of the entry with a nonce. The first N bits of the hash must be zeros.
This nonce can be up to 8 bytes, and is then stored with the transaction. The N
bits can be changed. If the \gls{mempool} is filling up too quickly, nodes can
increase the difficulty.

Instead of being economically expensive to execute a DOS attack, PADLOCK makes
it very computationally expensive.

\section{Conclusion}
PADLOCK is a blockchain system designed to allow for a high throughput, as well as increased
privacy. All the blockchain does, is allow for checking if a coin has already
been spent. This is the minimum for a functioning digital currency. Because of
this, transactions take very little disk space, allowing a very high throughput.
\Gls{ASIC} resistance is achieved through algorithm switching.  Due to
transactions not being publicly disclosed on chain, PADLOCK achieves a high level of
privacy. DOS attacks can be countered by requiring proof of work to be submitted
with each transaction. All this together creates a very robust base for a
digital currency.

\clearpage

\printglossaries

\end{document}
